### 2017-01-22 text/Chapter02.tex
Edit pages 188-208

The theoretical parts of this thesis extend the work of Uustalu and Vene who use comonads
to give the semantics of dataflow computations \cite{comonads-dataflow} and more generally,
notions of \emph{context-dependent computations} \cite{comonads-notions}. The computations discussed
in the latter work include streams, arrays and containers. This is a more diverse set of examples,
but they all mostly represent forms of collections. Ahman et al. \cite{comonads-containers} discuss
the relation between comonads and \emph{containers} \cite{types-containers} in more details.

>>>>

The theoretical parts of this thesis extend the work of Uustalu and Vene who use comonads
to give the semantics of dataflow computations \cite{app-dataflow-essence} and more generally,
notions of \emph{context-dependent computations} \cite{comonads-notions}. The computations discussed
in the latter work include streams, arrays and containers. This is a more diverse set of examples,
but they all mostly represent forms of collections. Ahman et al. \cite{comonads-containers} discuss
the relation between comonads and \emph{containers} \cite{types-containers} in more details.
